---
title: "MT_project"
author: "Xiangxiong Feng"
date: "2023-10-23"
output: github_document
---

```{r,echo=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(rvest)
library(readxl)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#Problem one


```{r, echo=FALSE}
zip_code =
  read.csv('data/Zip Codes.csv') |>
  mutate(borough = County.Name)|>
  rename(ZIPCODE = ZipCode)

change_address_2018 = 
  read_excel('data/USPS CHANGE OF ADDRESS NYC.xlsx', sheet = 1)
change_address_2019 = 
  read_excel('data/USPS CHANGE OF ADDRESS NYC.xlsx', sheet = 2)
change_address_2020 = 
  read_excel('data/USPS CHANGE OF ADDRESS NYC.xlsx', sheet = 3)
change_address_2021 = 
  read_excel('data/USPS CHANGE OF ADDRESS NYC.xlsx', sheet = 4)
change_address_2022 = 
  read_excel('data/USPS CHANGE OF ADDRESS NYC.xlsx', sheet = 5)

change_address = 
  bind_rows(change_address_2018,change_address_2019,change_address_2020,change_address_2021,change_address_2022)|>
  separate(MONTH, into = c('year','month'), sep = 4)|>
  mutate(
    month = str_replace(month,'\\-',''),
    net_change = `TOTAL PERM IN`- `TOTAL PERM OUT`)|>
  separate(month, into = c('month', 'day'),sep = 2 )|>
  select(-day)
  

```


The two raw datasets include 'USPS CHANGES OF ADDRESS NYC' and 'Zip Codes'.
The 'USPS CHANGES OF ADDRESS NYC' shows the aggregate Change of Address (COA) data
in New York City between 2018 and 2022. The data includes `r ncol(change_address)`variables such as zip code. There are total `r nrow(change_address)` observations. The 'Zip Codes' is a supplementary dataset which has important variables such as name of county and its neighborhood. There are `r ncol(zip_code)` variables and `r nrow(zip_code)`observation.


```{r, echo=FALSE}
#data combination
full_data = 
  full_join(change_address,zip_code, by ='ZIPCODE')


#number of unique zipcode
full_data |>
  select(ZIPCODE)|>
  distinct()|>
  count()
  
#number of unique neighborhood
full_data |>
  select(Neighborhood)|>
  drop_na()|>
  distinct()|>
  count()
  


```
#
```{r, echo=FALSE}
full_data |>
  filter(borough == 'Queens')|>
  group_by(CITY)|>
  summarise(Count = n())|>
  arrange(desc(Count))|>
  knitr::kable()

full_data |>
  filter(borough == 'New York')|>
  group_by(CITY)|>
  summarise(Count = n())|>
  arrange(desc(Count))|>
  knitr::kable()
```
There are 60 months between 2018 and 2022. However, some of ZIP codes have fewer 60 observations. The reason is that the records of some  ZIP codes for cerain months are missing in raw COA data.  Moreover, most of these are also missing neighborhood values, which are not given by the origin Zip Codes data. For example, the records for ZIP code 10008 for certain months are missing, and this ZIP cod has fewer 60 observations. The neighborhood of this Zip code is also missing.


# problem 2

```{r, echo=FALSE}
#table showing the average of net_change in each borough and year
full_data |>
  group_by(borough, year)|>
  summarize(Average_net_change = mean(net_change))|>
  drop_na()|>
  knitr::kable(digits = 2)
  

  
```

A table showing the average of `net_change` in each borough and year is created. From this table, we can see that the overall average net change keeps getting more negative from 2018 and reach an unusual peak around 2020, then it begins to return to normal level. The overall population size is dercreasing.


```{r, echo=FALSE}
#a table showing, across all observed data, the five lowest values of net_change
full_data |>
  arrange(net_change)|>
  head(5)|>
  select(ZIPCODE, Neighborhood, year, month, net_change)|>
  knitr::kable()
```

The table above shows the five lowest values of net change. We can see that all see that all these five observation are made in 2020, which is corresponding to our last table. The neighborhood of three observation are 'Gramercy Park and Murray Hill'.

```{r, echo=FALSE}
full_data |>
  filter(year%in% c('2018', '2019'))|>
  arrange(desc(net_change))|>
  head(5)|>
  select(ZIPCODE, Neighborhood, year, month, net_change)|>
  knitr::kable()
```
The table above shows the five highest values of net change across data observed before 2020.


```{r, echo=FALSE}
overall_average_net_change =
  full_data|>
  group_by(borough, month,Neighborhood)|>
  summarize(Average_Net_Change = mean(net_change))|>
  drop_na()|>
  ggplot(aes(x= month, y= Average_Net_Change))+ geom_point(aes(color = borough))+
  facet_grid(.~borough)+
  labs(title = 'overall average net change across boroughs')
overall_average_net_change
ggsave("results/overall_average_net_change.pdf", overall_average_net_change, width = 8, height = 5)
```




```{r, echo=FALSE}
wordcountaddin::text_stats("mt_project.Rmd")
```


