---
title: "MT_project"
author: "Xiangxiong Feng"
date: "2023-10-23"
output: html_document
---

```{r}
library(tidyverse)
library(ggridges)
library(patchwork)
library(rvest)
library(readxl)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#Problem one
```{r}
#upload data
change_address = 
  read_excel('data/USPS CHANGE OF ADDRESS NYC.xlsx')
zip_code = 
  read.csv('data/Zip Codes.csv')
```

The two raw datasets include 'USPS CHANGES OF ADDRESS NYC' and 'Zip Codes'.
The 'USPS CHANGES OF ADDRESS NYC' shows the aggregate Change of Address (COA) data
in New York City between 2018 and 2022. The data includes factors about date, zip code, city, total prem out and total prem in. There are total `r nrow(change_address)` observations. The 'Zip Codes' is a supplementary dataset which has important factors such as name of county and its neighborhood. There are `r ncol(zip_code)` factors and `r nrow(zip_code)`observation.




